Refinements for open automata

### 2023-01-26 2021-Refinement/paper/refinementarticleV2.tex
TODOs

Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
\begin{align*}		
J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
\end{align*}

@@

\item  Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
By transitivity with the second hypothesis we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
That implies:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
which gives us what we needed to demonstrate. \qed

>>>>

Recall in this case \LUDO{ WHICH CASE???}  $k \notin J'_1$, $\forall x \in X$ we have
\begin{align*}		
J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
\end{align*}

@@

\item \LUDO{ OLD OUTDATED PROOF?????} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
\end{multline*}
We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
\end{multline*}
By transitivity with the second hypothesis we obtain:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
That implies:
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
\end{multline*}
which gives us what we needed to demonstrate.} \qed
